Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Fixed a ref. Changed font size, looks more readable to me that way.

---
title: Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th
 Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
subtitle: Universities of Leipzig and Maryland
author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran). Through network analysis, it was possible to draw first conclusions about the acquired data.
toc: no
fontsize: 11pt
lang: en
documentclass: article
geometry: margin=1.25in
urlcolor: blue
bibliography: paper.bib
csl: aethiopistische-forschungen.csl
---

>>>>

---
title: Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th
 Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
subtitle: Universities of Leipzig and Maryland
author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran). Through network analysis, it was possible to draw first conclusions about the acquired data.
toc: no
fontsize: 12pt
lang: en
documentclass: article
geometry: margin=1.25in
urlcolor: blue
bibliography: paper.bib
csl: aethiopistische-forschungen.csl
---
